\label{sec:derivation}

Here the mathematical model used in Suzerain to simulate reacting flows is
presented.

\subsection{Conservation laws}

This section extends the Favre-averaged slow growth equations to
chemically reacting flows.  Following~\cite{Anderson_hypersonics,
  Kirk_2009_FINS_model_doc,
  Topalian_2011_temporal_slow_growth_reacting}, the conservation of
mass, momentum, and total energy for a compressible fluid composed of
$N_s$ constitutive components may be written as
%
\begin{align*}
  \pp{\rho_{\alpha}}{t} & + \pp{}{x_j} (\rho_{\alpha} u_j + \rho_{\alpha} v_{\alpha, j}) = \dot{\omega}_{\alpha}, \\
  \pp{\rho}{t} & + \pp{}{x_j} (\rho u_j) = 0, \\
  \pp{\rho u_i}{t} & + \pp{}{x_j} (\rho u_j u_i + p \delta_{ji} - \tau_{ji}) = 0, \\
  \pp{\rho E}{t} & + \pp{}{x_j} \left(\rho u_j H + \sum_{\alpha=1}^{N_s} \rho_{\alpha} v_{\alpha, j} h_{\alpha}  - \tau_{ji} u_i + q_j \right) = 0,\\
\end{align*}
% 
where $\rho_{\alpha}$ is the density of species $\alpha$, $\rho=\sum_{\alpha} \rho_{\alpha}$
is the mixture density, $u_i$ is the mixture velocity in the $i$th
direction, $v_{\alpha, i}$ is the diffusion velocity of species $\alpha$ in the
$i$th direction, $E$ is the total energy per unit mass, $p$ is the
pressure, $H$ is the total enthalpy per unit mass, $\tau_{ji}$ is the
viscous stress tensor, and $q_j$ is the heat flux vector.  Note that
Roman indices ($i$, $j$) indicate spatial directions.  For these,
repeated indices imply summation.  Greek indices ($\alpha$) indicate
species, and repeated Greek indices do not imply summation.

Further note that there are more governing equations here than
unknowns.  This is resolved by the consistency between the
conservation of mass equation and the species conservation equations.
However, we must choose what set of equations to model and discretize.
Here, we choose to include the conservation of mass equation and $N_s
-1$ species conservation equations.  Further, the state variables will
be $\rho$, $\rho_{\alpha}$ for $\alpha \in 1, \ldots, N_s -1$, $\rho
u_i$ for $i = 1, 2, 3$, and $\rho E$.  Thus, we have $N_s + 4$ state
variables.

\subsection{Constitutive relations and other assumptions}
\label{sec:constitutive}

\subsubsection{Mass Diffusion}
Species diffusion is modeled using Fick's law combined with the
self-consistent effective binary diffusion model of Ramshaw~\cite{?}.
Specifically, Fick's law is given by
%
\begin{equation*}
\rho_{\alpha} v_{\alpha, i} = - \rho \mcal{D}_{\alpha} \pp{c_{\alpha}}{x_i},
\end{equation*}
% 
where $\mcal{D}_{\alpha}$ is the mass diffusivity for species
$\alpha$ and $c_{\alpha}$ is the mass fraction $\rho_{\alpha} / \rho$.
These mass diffusivities depend only on the state and will be computed
using Antioch.

Given that the $\mcal{D}_{\alpha}$ values are in general different for
each $\alpha$, the Fickian model is not guaranteed to satisfy mass
conservation.  That is,
%
\begin{equation*}
\sum_{\alpha = 1}^{N_s} \rho_{\alpha} v_{\alpha, i} = - \rho \sum_{\alpha = 1}^{N_s} \mcal{D}_{\alpha} \pp{c_{\alpha}}{x_i} \neq 0,
\end{equation*}
% 
leading to an extra term in the implied conservation of mass
equation.

To alleviate this problem, Ramshaw~\cite{?} devised the self-consistent
effective binary diffusion model.  In this model, each flux is
corrected as follows:
%
\begin{equation*}
\rho_{\alpha} v_{\alpha, i} = - \rho \mcal{D}_{\alpha} \pp{c_{\alpha}}{x_i} + c_{\alpha} \sum_{\beta = 1}^{N_s} \rho \mcal{D}_{\beta} \pp{c_{\beta}}{x_i}.
\end{equation*}
% 
Since $\sum_{\alpha} c_{\alpha} = 1$, this form clearly gives
$\sum_{\alpha} \rho_{\alpha} v_{\alpha,i} = 0$.

\subsubsection{Chemical Reactions}
The source terms $\dot{\omega}_{\alpha}$ in the species equations
appear due to chemical reactions.  At a given point in space and time,
these sources depend only on the state at that point in space and
time.  These terms will be evaluated from reaction mechanisms and
reaction rate models implemented in Antioch~\cite{?}.  The details of
these models will not be discussed further here.

\subsubsection{Viscous Stress}
The viscous stress is given by
%
\begin{equation*}
\tau_{ij} =  2 \mu \left[ \frac{1}{2} \left(\pp{u_i}{x_j} + \pp{u_j}{x_i} \right) - \frac{1}{3} \pp{u_k}{x_k} \delta_{ij} \right].
\end{equation*}
% 
Velocity derivatives are easily computed from the state derivatives,
and the viscosity $\mu$ is computed via a call to Antioch.

\subsubsection{Heat Flux}
The heat flux is given by
%
\begin{equation*}
q_j = - \kappa \pp{T}{x_j}.
\end{equation*}
% 
The temperature gradient is not easy to compute from derivatives of
state because an explicit functional form for the temperature given
the state is not available.  Thus, we will proceed by computing the
temperature field in physical space, transforming back to wave space,
differentiating, and transforming to physical space again.

The thermal conductivity is computed via a call to Antioch.

\subsubsection{Pressure}
The mixture pressure is a sum of the species partial pressures:
%
\begin{equation*}
p = \sum_{\alpha = 1}^{N_s} p_{\alpha}.
\end{equation*}
%
Each partial pressure is computed from the ideal gas law,
%
\begin{equation*}
p_{\alpha} = \rho_{\alpha} R_{\alpha} T,
\end{equation*}
% 
where $R_{\alpha}$ is the gas constant for the species $\alpha$.
These values can by obtained from Antioch.

\subsubsection{Species Enthalpies}
Species enthalpies are determined using Antioch.

\subsection{Transforms}
This section examines trips between wave and physical space.

The wave to physical space transforms are summarized in
Table~\ref{tbl:w2p}.
%
\begin{table}[ht]
\caption{Wave to physical.  NOTE: This count is tentative.}
\begin{tabular}{|c|c|}
\hline
Quantity & \# of Fields \\
\hline
\hline
$\rho$ & 1 \\
$\rho_{\alpha}$ & $N_s - 1$ \\
$\rho u_i$ & 3 \\
$\rho E$ & 1 \\
$\pp{\rho}{x_j}$ & 3 \\
$\pp{\rho_{\alpha}}{x_j}$ & $3 (N_s - 1)$ \\
$\pp{\rho u_i}{x_j}$ & 9 \\
$\pp{T}{x_j}$ & 3 \\
\hline
Total & $4(N_s + 4)$\\
\hline
\end{tabular}
\label{tbl:w2p}
\end{table}
% 
Note that this does \emph{not} include the energy derivatives
($\partial \rho E / \partial x_j$).  Need to make sure this is
correct.

The physical to wave space transforms are summarized in
Table~\ref{tbl:p2w}.
%
\begin{table}[ht]
\caption{Physical to wave.  NOTE: This count is tentative.}
\begin{tabular}{|c|c|}
\hline
Quantity & \# of Fields \\
\hline
\hline
Sources ($\dot{\omega}_{\alpha}$ \& SG) & $N_s + 4$ \\
Fluxes & $3 (N_s +4)$ \\
T & 1 \\
\hline
Total & $4(N_s + 4) + 1$\\
\hline
\end{tabular}
\label{tbl:p2w}
\end{table}
% 


\subsection{Slow growth models}
\label{sec:slowgrowthmodels}
A useful approach to perform DNS on some turbulent flow configurations where the
flow develops in space or time is to perform a homogenization, using the
assumption of slow variation (or slow growth) of the mean and rms quantities
as related to the fast variation of turbulent fluctuations. This
homogenization procedure allows to simulate the turbulent flow at a specific
stage of the development in space or time. Examples of these procedures are the
works of Spalart ~\citep{Spalart1988Direct} for incompressible boundary layers,
and of Venugopal ~\citep{Venugopal2003} for channel flow with wall injection.
In practice, the slow growth approach introduces source terms in the
Navier--Stokes equations, were their functional form are specific to the flow
configuaration that was homogenized and on modeling assumption. These slow
growth sources will be generically designated with $\Ssd$.


\subsection{Dimensional equations}
\label{sec:dimensionalmodelequations}

By combining the conservation laws with our constitutive relations
and assumptions, we arrive at the dimensional equations
\todo{Put reacting flow equations here.}




